Relative Stable Maps in Genus One via Radial Alignments

### 2017-12-17 genus-one-relative-maps.tex
More thing on line bundle

It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.

@@

Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$. Finally, suppose that $f$ is not constant on $C_0$. The picture is:

@@

Fix $i =1,\ldots,k$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
\begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}

>>>>

It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then gluing.

@@

Suppose furthermore that $C_0$ is a non-contracted \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$. The picture is:

@@

Fix $i =1,\ldots,k$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
\begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}
We now blow-up the surface $W$ at the points $(q_i,0)$ with weight $r_i$ in the horizontal direction and weight $1$ in the vertical direction: if $x_i$ is a local co-ordinate for the fibre around $q_i$, this means that we blow-up in the ideal $(x_i,t^{r_i})$.

The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre isomorphic to $C_0$ and central fibre isomorphic to $C$. The total space of $W^\prime$ is no longer smooth, but this is fine; the projection to $\Aaff^1_t$ is still flat. The central fibre is a linearly trivial Cartier divisor:
\begin{equation*} W^\prime_0 = C_0 + C_1 + \ldots + C_k = 0 \in \Pic W^\prime \end{equation*}
The $C_i$ are not themselves Cartier, but $r_i  C_i$ is Cartier for $i=1,\ldots,k$. We have:
\begin{equation*} r_i C_i \cdot C_0 = 1 \end{equation*}
Now, let $x_1,\ldots,x_n$ denote the marked points of $C$. These are divisors on the central fibre $W^\prime_0$, and hence can be extended to divisors $\tilde{x}_1,\ldots,\tilde{x}_n$ on $W^\prime$. Consider the line bundle:
\begin{equation*} \tilde{L} = \OO_{W^\prime}(\beta C_0 + \Sigma_{i=1}^n \alpha_i \tilde{x}_i) \end{equation*}
Note that $\beta C_0$ is indeed a Cartier divisor, since
\begin{equation*} \beta C_0 = - \sum_{i=1}^k \beta C_i = - \sum_{i=1}^k m_i (r_i C_i) \end{equation*}
and the $r_i C_i$ are Cartier. We claim that when we restrict $\tilde{L}$ to the central fibre we recover the line bundle $L = f^* \OO(1)$ that we started with.

For $i=1,\ldots,k$, we have:
\begin{align*} \tilde{L}|_{C_i} & = \OO_{C_i} \left( \beta (C_0 \cdot C_i) q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right) \\
& = \OO_{C_i} \left( (\beta/r_i) q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right)\\
& = \OO_{C_i} \left( m_i q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right) \\
& = L|_{C_i} \end{align*}
On the other hand
\begin{align*} \tilde{L}|_{C_0} & = \OO_{C_0} \left( - \sum_{i=1}^k \beta (C_i \cdot C_0) q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) \\
& = \OO_{C_0} \left( - \sum_{i=1}^k m_i q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) \\
& = L|_{C_0} \end{align*}
and the fact that $\tilde{L}|_{W^\prime_0} = L$ follows from the fact that the dual intersection graph of $C$ has genus zero.

Now, $\tilde{L}$ comes with a unique section whose restriction to $W^\prime_0 \cong C$ is $s_0$. After we extend the sections $s_1,\ldots,s_N$, it is clear that the resulting stable map is in the nice locus (i.e. that it is not mapped into $H$).

Now, to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions is:
\begin{equation*} \HH^1(C,L) \end{equation*} \marginpar{Is this true even when $C$ is reducible}
By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain:
